\thesistitle

### 2019-06-13 sections/research.tex
About clone detection in general

>>>>

The overall process regarding clone detection is displayed in figure \ref{fig:clonedetection}. First of all, we use JavaParser to read a project from disk and build an AST, one class file at a time. Each AST is then converted to a grid that maps relations between statements, further explained in section \ref{sec:clonegrid}. On basis of this grid, we detect clone classes and verify them using three thresholds (in order of importance):
\begin{itemize}
  \item Amount of tokens.
  \item Amount of statements.
  \item Amount of lines.
\end{itemize}
If the detection was configured to detect either type 2R, 3 or 3R clones we perform some type specific transformations on the resulting set of clones.

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{img/CloneDetection}
  \caption{CloneRefactor clone detection process.}
  \label{fig:clonedetection}
\end{figure}

\subsubsection{Generating the clone grid}\label{sec:clonegrid}
